Spatiotemporal models of species biomass split by maturity class

### 2019-09-06 analysis/VOCC/1-biomass-models.Rmd
housekeeping

# # Species run so far...
# species <- "Arrowtooth Flounder"
#species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
# species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # using all data for maturity thresholds
# species <- "Quillback Rockfish" # no maturity classes and WCHG not work
# species <- "Pacific Ocean Perch" 
 species <- "Yelloweye Rockfish"
```

@@

>>>>

# # Species run so far...
# species <- "Arrowtooth Flounder"
# species <- "Petrale Sole"
# species <- "English Sole"
# species <- "Dover Sole" # maturity data error for WCHG
# species <- "Southern Rock Sole"
# species <- "Flathead Sole"

# species <- "Walleye Pollock"
# species <- "Pacific Cod"
# species <- "Pacific Ocean Perch"

# species <- "Silvergray Rockfish"
# species <- "Quillback Rockfish"
# species <- "Yelloweye Rockfish"
# species <- "Bocaccio"
# species <- "Sharpchin Rockfish"
# species <- "Splitnose Rockfish"
# species <- "Canary Rockfish"
# species <- "Rougheye/Blackspotted Rockfish Complex"
 species <- "Redbanded Rockfish"
# species <- "Greenstriped Rockfish"

# species <- "Longspine Thornyhead"
# species <- "Shortspine Thornyhead",
# species <- "Sablefish"
# species <- "Lingcod"

# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
# species <- "Longnose Skate"
 species <- "Spotted Ratfish"

```

@@

  if (region == "All synoptic surveys") {
    spde <- sdmTMB::make_spde(data$X, data$Y, n_knots = 500)
  }
